Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-11-03 paper.tex
UP

\section{Results and Analysis}\label{results_analysis}
\subsection{Comparision Test}\label{comparisionTest}

In this section, we analyse the composition solution generated by using our approach. In particularly, we show that our proposed approach can produce solutions that results better matchmaking , which meets user's goal better.

Now we look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ defined in the solution model using black-box testing for the comparison, where the comprehensive quality awareness approach and QoS awareness approach \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is in a decision table shown in Table \ref{decisionTable}. Solutions to five tasks are compared using two evaluation models in WSC09. In each task, we compare $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$, and $Q_{QoS}$ is normalised to make it comparable to another method in our comprehensive awareness approach

@@

>>>>

\section{Results and Analysis}\label{results_analysis}
\subsection{Comparison Test}\label{comparisonTest}

In this section, we analyse the composition solution generated by using our approach. In particularly, we show that our proposed approach can produce solutions that results better matchmaking , which meets user's goal better.
Now we look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ defined in the solution model using black-box testing for the comparison, where the comprehensive quality awareness approach and QoS awareness approach \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is in a decision table shown in Table \ref{decisionTable}. Solutions to five tasks are compared using two evaluation models in WSC09. In each task, we compare $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$, and $Q_{QoS}$ is normalised to make it comparable to another method in our comprehensive awareness approach

@@

To visually compare the results generated from two evaluation approaches, we demonstrate the differences of composition weighted graphs under two different methods. The Figure \ref{comparison} shows two composition weighted graphs, which are the solutions to Task 3 for comprehensive quality-aware and QoS-aware web service composition respectively. The two weighted graphs have exactly the same workflow structure, in which the different service vertex and edges are denoted in red for making a comparison.

\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=8cm]{comparision.pdf}}}
 \caption{Example Comparison of solutions to Task 3 under different approaches.}
 \label{comparison}
\end{figure}
